Adaptive Distance Metric Selection for Supervised Classification

### 2016-10-21 latex/Adaptive_distance_metric_notes.tex
add

>>>>

\section{Plot of number of outliers as function $\epsilon$}

\todo[inline]{Task 1: this should be done before next meeting on 2016-10-27}

\todo[inline]{Task 2: make a plots a number of outliers as function of epsilon
+ show also the datasets which you have used and so on}

\todo[inline]{Task 3: try different datasets, also generate the two gaussian mixtures}

\todo[inline]{Task 4: find out how to export figure to EPS from AIMMS}
